Multi-line Intensity Mapping

### 2019-06-20 paper/ms.tex
Add intrinsic spatial fluctuations

>>>>

To model the intrinsic spatial fluctuations of each line, we follow
\citet{2016ApJ...825..143L} and \citet{2016ApJ...832..165C}, though we adopt
the notation of the former. We use the word ``intrinsic'' here not to mean the
signal in the cosmological rest frame, but rather the observed signal assuming
the observed coordinates have been transformed to comoving coordinates with
the correct redshift. This is not the case for interloping lines, for which
their contribution to the signal is distorted because the assumed redshift and
the emitted redshift are not the same.

The intrinsic emission from a line $i$ is given by
\beq\label{eq:int_ps}
P_{i,i}(k, \mu, z) = \avg{I_i}^2 \avg{b_i}^2 (1 + \beta_i \mu^2)^2 
              D\left[\mu k \sigma_p(z)\right] P_{\delta, \delta}(k, z)
              + P_{i, \text{shot}}\text{,}
\eeq
where $\mu=k_{\parallel}/k$ is the cosine of the angle between the wavevector
$\bm{k}$ and the line of sight direction, $\avg{I_i}$ is the average specific
intensity of line $i$, and $\avg{b_i}$ is the average luminosity-weighted bias
of the emitting galaxies. The Kaiser effect {\bf Kaiser 1987} is implemented
through the $(1 + \beta_i \mu^2)^2$ factor, where $\beta_i =
f_{\Omega}/\avg{b_i}$ with $f_{\Omega} = \text{d}\ln{D}/\text{d}\ln{a}$ is the
logarithmic derivative of the growth factor, well approximated by $f_{\Omega}
\approx \Omega^{0.55}$ {\bf Linder 2005}. We assume a Lorentzian form for the
finger-of-god suppression:
\beq\label{eq:fog}
D(x) = \frac{1}{1+x^2}\text{.}
\eeq
We approximate the pairwise velocity dispersion by $\sigma_p(z) =
\sigma_v(z)/\sqrt{2}$ with $\sigma_v^2(z)$ being the variance of the
line-of-sight component of the velocity field according to linear theory. We
use the {\bf Eisenstein and Hu 1998} model for the linear theory matter power
spectrum, $P_{\delta,\delta}(k, z)$. The computation of the shot noise,
$P_{i,\text{shot}}$ is given in Appendix~\ref{app:co_int}. All basic
cosmological calculations are performed using the code \texttt{colossus} {\bf
Diemer 2018}.
